---
title: "Distributed Generation in Brazil"
author: "Andre Moura Gomes da Costa"
date: "November 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This website contains a briev exploration report about the distributed generation (DG) on Brazil. Two aspects are shown: The growth of DG over time and the situation over the country area.

### Data obtention

Data was obtained from the ANEEL (Brazilian National Agency of Electric Energy) DG register database, available in the [ANEEL website](http://www.aneel.gov.br/outorgas/geracao/-/asset_publisher/mJhnKIi7qcJG/content/registro-de-central-geradora-de-capacidade-reduzida/655808?inheritRedirect=false&redirect=http%3A%2F%2Fwww.aneel.gov.br%2Foutorgas%2Fgeracao%3Fp_p_id%3D101_INSTANCE_mJhnKIi7qcJG%26p_p_lifecycle%3D0%26p_p_state%3Dnormal%26p_p_mode%3Dview%26p_p_col_id%3Dcolumn-2%26p_p_col_pos%3D1%26p_p_col_count%3D2)

The site was scraped with a function displayed in the end of this website 

### Evolution

The following figures show the growth of PV on Brasil. It can be seen that it has presented an exponential growth, both for units installed and for power installed. Regarding units installed, a change on the growth rate can be seen on June of 2016, when regulations have changed.

```{r , echo=FALSE, warning=F, fig.width=6, fig.height=3, message=F}
library(leaflet)
library(dplyr)
library(lubridate)
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}


load(file="latlong.RData")
```

```{r , echo=FALSE, warning=F, fig.width=6, fig.height=3, message=F}

LatLongSol<- mutate(filter(LatLong,fonte =="Radiação solar"), 
                    Date= dmy(data_conexao)) %>%
     arrange(Date) %>% mutate (count=1:44827, 
                               dumb=1,
                               potencia_instalada_k_w=gsub("\\.","",potencia_instalada_k_w),
                               Pot = as.numeric(gsub(",",".",potencia_instalada_k_w)),
                             P_cumul=cumsum(Pot))

LatLongSolM <- filter(LatLongSol,Date>ymd("2014/01/01"))%>%
    mutate(ano=year(Date))%>%
    group_by(ano) %>%
    summarise(media=mean(Pot),
              mediana=median(Pot))

mod1<-lm(data=filter(LatLongSol,Date>ymd("2015/01/01") & 
                   Date<ymd("2016/07/01") &
                   fonte =="Radiação solar"),
   log10(count)~Date)

LatLongSol$mod1<-predict(mod1, newdata = LatLongSol)

mod2<-lm(data=filter(LatLongSol,Date>ymd("2016/07/01") & 
    #               Date<ymd("2016/06/01") &
                   fonte =="Radiação solar"),
   log10(count)~Date)
LatLongSol$mod2<-predict(mod2, newdata = LatLongSol)


library(ggplot2)
p2<-ggplot(data=filter(LatLongSol,Date>ymd("2014/01/01") ),#&# fonte =="Radiação solar"),
       aes(x=Date,y=log10(cumsum(dumb))))+
    geom_line()+
    theme_light()+
    ylab(expression(Log[10]))+
 #   theme(axis.title.y=element_blank(),
 #       axis.text.y=element_blank())+
    xlab("Data")+
    geom_line(aes(y=mod1),col="red",linetype=2)+
    geom_line(aes(y=mod2),col="blue",linetype=2)



p1<-ggplot(data=filter(LatLongSol,Date>ymd("2014/01/01") & fonte =="Radiação solar"),
       aes(x=Date,y=(cumsum(dumb))))+
    geom_line()+
    theme_light()+
    ylab("Total DG Units Installed")+
  #  geom_area(fill="blue")+
    xlab("Data")

multiplot(p1, p2, cols=2)

mod2pot<-lm(data=filter(LatLongSol,Date>ymd("2016/07/01")),
   log10(P_cumul)~(Date))

LatLongSol$mod2pot<-predict(mod2pot, newdata = LatLongSol)

p2<-ggplot(data=filter(LatLongSol,Date>ymd("2014/01/01")),
    aes(x=Date,y=log10(P_cumul)))+
    geom_line()+
    theme_light()+
    ylab(expression(Log[10]))+
 #   theme(axis.title.y=element_blank(),
 #       axis.text.y=element_blank())+
    xlab("Data")+
    geom_line(aes(y=mod2pot),col="red",linetype=2)

p1<-ggplot(data=filter(LatLongSol,Date>ymd("2014/01/01")),
       aes(x=Date,y=P_cumul))+
    geom_line()+
    theme_light()+
    ylab("Total DG Installed power")+
  #  geom_area(fill="blue")+
    xlab("Data")

multiplot(p1, p2, cols=2)

p1<-ggplot(data=LatLongSolM,
       aes(x=ano,y=media))+
    geom_line()+
    theme_light()+ 
  #  geom_line(aes(x=ano,y=mediana),col='blue')+
    ylab("Potência Instalada Média")+
  #  geom_area(fill="blue")+
    xlab("Ano")

p2<-ggplot(data=LatLongSolM,
       aes(x=ano,y=mediana))+
    geom_line()+
    theme_light()+ 
#    geom_line(aes(x=ano,y=mediana),col='blue')+
    ylab("Mediana da Potência Instalada")+
  #  geom_area(fill="blue")+
    xlab("Ano")

#multiplot(p1, p2, cols=2)

```

### Location

The following maps show the units installed over the country and, the total power installed by country.

```{r , echo=F, , fig.width=6, fig.height=3, message=F}
my_map <- LatLong %>% leaflet()%>%
   addTiles()%>%
    addMarkers(lat=LatLong$lat,
               lng=LatLong$lng,
               clusterOptions=markerClusterOptions())
my_map

LatLongCity <-LatLong %>% group_by(uf) %>% 
    summarise(Pot=sum(Pot,na.rm=T), lat=median(lat,na.rm=T),lng=median(lng,na.rm=T))

my_map <- LatLongCity %>% leaflet()%>%
   addTiles()%>%
    addCircles(lat=~lat,
               lng=~lng,
               radius = ~sqrt(Pot)*1000, 
               weight = 1,
               popup = ~uf)
my_map
```
```



```{r function}
get_power_info <- function(pagina = 1L, acao = "buscar", login = "",
                           nom_pessoa = "", id_agente = "", dat_conexao_inicio = "",
                           dat_conexao_fim = "") {
    
    # we need alot of packages to make this work
    
    suppressPackageStartupMessages({
        require("httr", quietly = TRUE, warn.conflicts = FALSE)
        require("xml2", quietly = TRUE, warn.conflicts = FALSE)
        require("rvest", quietly = TRUE, warn.conflicts = FALSE)
        require("janitor", quietly = TRUE, warn.conflicts = FALSE)
        require("stringi", quietly = TRUE, warn.conflicts = FALSE)
        require("dplyr", quietly = TRUE, warn.conflicts = FALSE)
    })
    
    # get the page like a browser
    
    httr::GET(
        url = "http://www2.aneel.gov.br/scg/gd/VerGD.asp",
        query = list(
            pagina = as.character(as.integer(pagina)),
            acao = acao,
            login = login,
            NomPessoa = nom_pessoa, 
            IdAgente = id_agente,
            DatConexaoInicio = dat_conexao_inicio,
            DatConexaoFim = dat_conexao_fim
        )
    ) -> res
    
    httr::stop_for_status(res)
    
    # DON'T PARSE IT YET
    
    out <- httr::content(res, as = "text")
    
    # Remove beginning & trailing whitespace from lines
    
    l <- stri_trim_both(stri_split_lines(out)[[1]])
    
    # Now, remove all form-component lines and all blank lines
    
    l[-c(
        which(grepl("<form", l, fixed = TRUE)), 
        which(grepl("<input", l, fixed = TRUE)),
        which(l == "")
    )] -> l
    
    # Get the indices of all the <td> tags that should have a <tr> before them but dont
    
    to_fix <- c()
    for (i in 1:(length(l)-1)) {
        if (all(c(
            grepl("/tr", l[i]), grepl("td", l[i+1])
        ))) {
            to_fix <- c(to_fix, (i+1))
        }
        
    }
    
    # Fix them
    
    l[to_fix] <- sprintf("<tr>%s", l[to_fix])
    
    # NOW WE CAN PARSE IT
    
    x <- read_html(paste0(l, collapse="\n"))
    
    # Find the table in a less breakable way
    
    tabl <- html_nodes(x, xpath=".//table[@class = 'tabelaMaior']/tr/td[contains(., 'UNIDADES')]/../..")
    
    # Remove the useless title row that makes html_table() cry
    
    xml_remove(html_node(tabl, xpath=".//tr[1]"))
    
    # Remove the bottom pagination row that makes html_table() cry
    
    xml_remove(html_node(tabl, xpath=".//tr/td[@colspan = '20']/.."))
    
    # Extract the table with better column names
    
    xdat <- html_table(tabl, header=TRUE, trim=TRUE)[[1]] 
    xdat <- janitor::clean_names(xdat)
    xdat <- dplyr::tbl_df(xdat)
    
    xdat
    
}

```
